An Expressive and Efficient Solution to the Service Selection Problem

### 2010-06-29 publicaciones/iswc10/paperISWC10-v4.tex
paperISWC10-v4

\begin{abstract}
Given the large number of Semantic Web Services that can be created from
online sources by using existing annotation tools, expressive formalisms and
efficient and scalable approaches to solve the service selection problem are
required in order to make this services widely available to the users.
In this paper, we propose such a framework that is grounded on logic and
the Local-As-View approach for describing instances of the service selection problem.
In our approach, Web services are semantically described using LAV mappings
in terms of generic concepts from an ontology, while the user requests correspond
to conjunctive queries on the generic concepts, that must be combined to solve
a task, plus a set of preferences that are used to rank the possible solutions.
The LAV formulation allows us to cast the service selection problem as a
query rewriting problem that must consider the relationships among the concepts
in the ontology and the ranks induced by the preferences of the user.
Then, building on related work, we devise an encoding of the resulting
query rewriting problem as a logical theory whose models are in correspondence
with the solutions of the user request, and in presence of preferences, whose
best models are in correspondence with the best-ranked solutions.
Thus, by exploiting known properties of modern SAT solvers, we provide an
efficient and scalable solution to the service selection problem.
The approach provides the basis to represent a large number of real-world
situations and interesting user requests.
\end{abstract}

@@

The semantic description of services is expressed following the
LAV paradigm in terms of mappings. These mappings describe the
services in terms of concepts in the domain ontology \cite{Ullman00}:
for each service $S_i$, there is a mapping that describes $S_i$
as a \emph{conjunctive query} on the concepts in the ontology that
also distinguish input and output attributes of the service.
For example, a service $S(x,y)$ that returns information about
flights originating at a given US city can be described with the view:
\[ S(\$x,y)\ \qrule\ \flight(x,y), \UScity(x)\,, \]
where $flight^2$ and $uscity^1$ are relational symbols in the
ontology. The symbol `\$' denotes that $x$ is an input attribute. 
The semantic interpretation of a mapping like this one enforces the following:
\begin{itemize}
\item the service represented by $S$ provides information in the
      form of tuples $(x,y)$,
\item the service is called with $x$ as input attribute and returns $(x,y)$,
\item each tuple $(x,y)$ returned by the service satisfies the rhs
      of the view; i.e., $\flight(x,y)$ and $\UScity(x)$, and
\item the views are not necessarily \emph{complete}; i.e., there may be
      other tuples $(x,y)$ that satisfy the rhs of the view but which
      are not available through $S$.
\end{itemize}

@@

In the third experiment, we test the system with ontologies of different sizes.
Ontologies corresponding to full binary trees of depth 2 to 7 were generated with
the predicate $\trip(x,y)$ at the root node. Then, for each node in the tree,
there is a view that is described by the predicate at that node.
The user request has the form
\[ Q(x_1,\ldots,x_4)\ \qrule\  \UScity(x_1),\,\trip(x_1,x_2),\,\trip(x_2,x_3),\,\trip(x_3,x_4),\,\trip(x_4,x_1).\]
In all cases, the compilation time was always less than 13 seconds.

>>>>

\begin{abstract}
Given the large number of Semantic Web Services that can be created from
online sources by using existing annotation tools, expressive formalisms and
efficient and scalable approaches to solve the service selection problem are
required in order to make these services widely available to the users.
In this paper, we propose such a framework that is grounded on logic and
the Local-As-View approach for describing instances of the service selection problem.
In our approach, Web services are semantically described using LAV mappings
in terms of generic concepts from an ontology, while the user requests correspond
to conjunctive queries on the generic concepts, that must be combined to solve
a task, plus a set of preferences that are used to rank the possible solutions.
The LAV formulation allows us to cast the service selection problem as a
query rewriting problem that must consider the relationships among the concepts
in the ontology and the ranks induced by the preferences of the user.
Then, building on related work, we devise an encoding of the resulting
query rewriting problem as a logical theory whose models are in correspondence
with the solutions of the user request, and in presence of preferences, whose
best models are in correspondence with the best-ranked solutions.
Thus, by exploiting known properties of modern SAT solvers, we provide an
efficient and scalable solution to the service selection problem.
The approach provides the basis to represent a large number of real-world
situations and interesting user requests.
\end{abstract}

@@

The semantic description of services is expressed following the
LAV paradigm in terms of mappings. These mappings describe the
services in terms of concepts in the domain ontology \cite{Ullman00}:
for each service $S_i$, there is a mapping that describes $S_i$
as a \emph{conjunctive query} on the concepts in the ontology that
also distinguish input and output attributes of the service.
For example, a service $S(x,y)$ that returns information about
flights originating at a given US city can be described with the view:
\[ S(\$x,y)\ \qrule\ \flight(x,y), \UScity(x)\,. \]
where $flight^2$ and $uscity^1$ are relational symbols in the
ontology. The symbol `\$' denotes that $x$ is an input attribute. 
The semantic interpretation of a mapping like this one enforces the following:
\begin{itemize}
\item the service represented by $S$ provides information in the
      form of tuples $(x,y)$,
\item the service is called with $x$ as input attribute and returns $(x,y)$,
\item each tuple $(x,y)$ returned by the service satisfies the rhs
      of the view; i.e., $\flight(x,y)$ and $\UScity(x)$, and
\item the views are not necessarily \emph{complete}; i.e., there may be
      other tuples $(x,y)$ that satisfy the rhs of the view but which
      are not available through $S$.
\end{itemize}

@@

In the third experiment, we test the system with ontologies of different sizes.
Ontologies corresponding to full binary trees of depth 2 to 7 were generated with
the predicate $\trip(x,y)$ at the root node. Then, for each node in the tree,
there is a view that is described by the predicate at that node.
The user request has the form:
\[ Q(x_1,\ldots,x_4)\ \qrule\  \UScity(x_1),\,\trip(x_1,x_2),\,\trip(x_2,x_3),\,\trip(x_3,x_4),\,\trip(x_4,x_1).\]
In all cases, the compilation time was always less than 13 seconds.
